Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-12 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: added comment to abhi on tick labels

%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
% General:
The detection of gravitational waves produced by coalescing compact binaries
allows us to explore the dynamical, nonlinear regime of general relativity
and to constrain modifications to it.
%
Some of these gravitational-wave events are detected with sufficiently high
signal-to-noise ratio, allowing us to probe the relaxation of the remnant black
hole to its final, stationary state -- the so-called black-hole ringdown,
characterized by a set of quasinormal modes.
% Main question:
Can we use the ringdown to constrain deviations to general relativity,
as predicted by several of its contenders?
% What we do:
Here, we take a first step to address this question, by using an
inspiral-merger-ringdown waveform model in the effective-one-body formalism,
augmented with a parametrization of the ringdown based on an expansion on the
final black hole's spin.
%
We give a prescription on to include to this waveform model the quasinormal mode frequencies
calculated on a theory-by-theory basis, in particular, for theories that deviate
from general relativity through higher-curvature corrections, namely,
Einstein-dilaton-Gauss-Bonnet, dynamical Chern-Simons, cubic- and quartic-order
effective-field-theories of general relativity.
%
% Main conclusion:
We confront the resultant waveform models against GW150914 and GW200129 data,
finding that while Einstein-dilaton-Gauss-Bonnet cannot be constrained with
these events, we can place upper bounds on the coupling constants of cubic-
($\ell_{\rm cEFT} \leqslant 38.2$~km) and quartic-order ($\ell_{\rm qEFT}
\leqslant 51.3$~km) effective-field-theories of general relativity, and
of dynamical Chern-Simons gravity ($\ell_{\rm CS} \leqslant 38.7$~km).
%
The latter result constitutes a concrete example of a theory presently
unconstrained by inspiral-only analyses which, however, can be constrained by
merger-ringdown studies.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure*}[t]
\includegraphics[width=0.9\textwidth]{figs/tmp_GW150914_intrinsic_params.pdf}
\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
detector-frame remnant mass $(1 + z) \, M_f$ for GW150914, using the same waveform model,
but without (blue contours)\agcomm{colors to be updated.} and with the non-GR parameters different from zero (orange contours, for
dCS gravity and $N_{\rm max}=0$). The contours represent 90\% credible levels.
%
We see that the introduction of the non-GR parameters does not bias the
inference on the source parameters.
}
\label{fig:corner_plot_all}
\end{figure*}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
% General:
The detection of gravitational waves produced by coalescing compact binaries
allows us to explore the dynamical, nonlinear regime of general relativity
and to constrain modifications to it.
%
Some of these gravitational-wave events are detected with sufficiently high
signal-to-noise ratio, allowing us to probe the relaxation of the remnant black
hole to its final, stationary state -- the so-called black-hole ringdown,
characterized by a set of quasinormal modes.
% Main question:
Can we use the ringdown to constrain deviations to general relativity,
as predicted by several of its contenders?
% What we do:
Here, we take a first step to address this question, by using an
inspiral-merger-ringdown waveform model in the effective-one-body formalism,
augmented with a parametrization of the ringdown based on an expansion on the
final black hole's spin.
%
We give a prescription on how to include to this waveform model the quasinormal mode frequencies
calculated on a theory-by-theory basis, in particular, for theories that deviate
from general relativity through higher-curvature corrections, namely,
Einstein-dilaton-Gauss-Bonnet, dynamical Chern-Simons, cubic- and quartic-order
effective-field-theories of general relativity.
%
% Main conclusion:
We confront the resultant waveform models against GW150914 and GW200129 data,
finding that while Einstein-dilaton-Gauss-Bonnet cannot be constrained with
these events, we can place upper bounds on the coupling constants of cubic-
($\ell_{\rm cEFT} \leqslant 38.2$~km) and quartic-order ($\ell_{\rm qEFT}
\leqslant 51.3$~km) effective-field-theories of general relativity, and
of dynamical Chern-Simons gravity ($\ell_{\rm CS} \leqslant 38.7$~km).
%
The latter result is a concrete example of a theory presently
unconstrained by inspiral-only analyses which, however, can be constrained by
merger-ringdown studies.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure*}[t]
\includegraphics[width=0.9\textwidth]{figs/tmp_GW150914_intrinsic_params.pdf}
\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
detector-frame remnant mass $(1 + z) \, M_f$ for GW150914, using the same waveform model,
but without (blue contours)\agcomm{colors to be updated.} and with the non-GR parameters different from zero (orange contours, for
dCS gravity and $N_{\rm max}=0$). The contours represent 90\% credible levels.
%
We see that the introduction of the non-GR parameters does not bias the
inference on the source parameters.
%
\hs{We also need to fix overlapping tick labels.}
}
\label{fig:corner_plot_all}
\end{figure*}
